Transitivity of Subtyping for Intersection Types

### 2019-06-23 papers/intersection-transitivity.tex
check

\begin{lemma}\label{lem:sub-inv-trans}
  If
  \begin{itemize}
  \item for any $C$ and $D$, if $C → D ∈ A$ and $\neg\,\mathsf{top}(D)$,
    then $C → D$ factors $B$, and
  \item $\neg\, \mathsf{topInCod}(A)$,
  \end{itemize}
  then $\dom{A} → \cod{A}$ factors $B$.
\end{lemma}
\begin{proof}
  The proof is by induction on $A$.
  \begin{itemize}
  \item Case $A$ is an atom. The statement is vacuously true.
  \item Case $A = A_1 → A_2$ is a function type. Then we conclude by applying
    the premise with $C$ and $D$ instantiated to $A_1$ and $A_2$ respectively.
  \item Case $A = A_1 ∩ A_2$.

    UNDER CONSTRUCTION
  \end{itemize}
\end{proof}

>>>>

\begin{lemma}\label{lem:sub-inv-trans}
  If
  \begin{itemize}
  \item for any $C$ and $D$, if $C → D ∈ A$ and $\neg\,\mathsf{top}(D)$,
    then $C → D$ factors $B$, and
  \item $\neg\, \mathsf{topInCod}(A)$,
  \end{itemize}
  then $\dom{A} → \cod{A}$ factors $B$.
\end{lemma}
\begin{proof}
  The proof is by induction on $A$.
  \begin{itemize}
  \item Case $A$ is an atom. The statement is vacuously true.
  \item Case $A = A_1 → A_2$ is a function type. Then we conclude by applying
    the premise with $C$ and $D$ instantiated to $A_1$ and $A_2$ respectively.
  \item Case $A = A_1 ∩ A_2$.  By the induction hypothesis for $A_1$
    and for $A_2$, we have that $\dom{A_1} → \cod{A_1}$ factors $B$
    and so does $\dom{A_2} → \cod{A_2}$.  So there exists
    $B_1$ and $B_2$ such that $B_1 ⊆ B$, $\neg\,\topInCod{B_1}$,
    $\dom{A_1} <: \dom{B_1}$, $\cod{B_1} <: \cod{A_2}$ and similarly
    for $B_2$. We need to show that $\dom{A} → \cod{A}$ factors
    $B$. We choose the witness $B_1 ∩ B_2$.  Clearly we have $B_1 ∩
    B_2 ⊆ B$ and $\neg \topInCod{B_1 ∩ B_2}$.  Also, we have
    \[
    \dom{B_1} ∩ \dom{B_2} <: \dom{A_1} ∩ \dom{A_2}
    \]
    and
    \[
    \cod{A_1} ∩ \cod{A_2} <: \cod{B_1} ∩ \cod{B_2}
    \]
    Thus, we have that $\dom{B_1 ∩ B_2} <: \dom{A}$
    and $\cod{A} <: \cod{B_1 ∩ B_2}$, and this case is complete.
  \end{itemize}
\end{proof}

We now turn to the proof of transitivity, that
if $A <: B$ and $B <: C$, then $A <: C$.
